\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-14 hoist.tex
hoisting at -Oz

\subsubsection{Profitability of hoisting loads}
A load instruction introduces a register where the value loaded will be kept,
the register pressure increases by one (unless the operand to load becomes dead
at the load). On the other hand, loading a value early will reduce the stall
during execution should the value is not in the cache. We generally prefer to
hoist load except the hoisting point is too far (this distance is computed by
looking at the experimental results of representative benchmarks, see
Section~\ref{sec:experimental-results}).

>>>>

When aggressively for code-size (at optimization level -Oz), we allow hoisting
of scalars even when the expression is not very busy. This creates unnecessary
computation on paths where the expression is not needed so the program may run slow
but reduces the code size. TODO: Experimental results.

\subsubsection{Profitability of hoisting loads}
A load instruction introduces a register where the value loaded will be kept,
the register pressure increases by one (unless the operand to load becomes dead
at the load). On the other hand, loading a value early will reduce the stall
during execution should the value is not in the cache. We generally prefer to
hoist load except when the hoisting point is too far (this distance is computed by
looking at the experimental results of representative benchmarks, see
Section~\ref{sec:experimental-results}).
